\vspace{-2cm}A generative model for urban firm networks

### 2020-09-02 main.tex

The rest of this paper is organized as follows: We first describe the generative model for urban networks and proceed to an empirical analysis of the network used as a case study. We then do a sensitivity analysis and exploration of the model on synthetic data. The model is calibrated on real European firm ownership data. We finally discuss implications of our results and possible extensions.

>>>>

The rest of this paper is organized as follows: we first describe the generative model for urban networks and proceed to an empirical analysis of the network used as a case study. We then do a sensitivity analysis and exploration of the model on synthetic data. The model is calibrated on real European firm ownership data. We finally discuss implications of our results and possible extensions.
